---
title: "bbrosterplots"
date: "`r Sys.Date()`"
output:
  rmarkdown::github_document:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{bbrosterplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

# Load package

```{r}
library(bbrosterplots)
library(dplyr)
```

## Read example data

```{r}
data(df_rosters) 
data(df_rosters1)

races <- unique(df_rosters$roster.name)
empty_out <- FALSE
```

## Required input data input format

The `bbrosterplots` packages expects input data that consists of 8 columns / variables, with pre-specified column names.

The `position` column naming requires the official roster position naming. It has some allowance for variants such as "Re-rolls" , "rerolls" and "Rerolls" .

PM add more detailed description of the input data format

```{r}
df_rosters %>% dplyr::filter(coach_name == "gsverhoeven")
```

# Add roster metadata

This adds:
* the cost for each player and inducement
* for each skill or skill stack a skill color

```{r}
df_rosters <- add_roster_metadata(df_rosters)

df_rosters %>% dplyr::filter(roster.name == "Gnome")
```

Subset races to speed up testing.

```{r}
races <- races[1:3]
df_rosters <- df_rosters %>%
  dplyr::filter(roster.name %in% races)

df_rosters1 <- df_rosters1 %>%
  dplyr::filter(roster.name %in% races)
```


## Create heatmap plots

```{r}
create_rosterplot(df_rosters, group_name = "Super league S6", tournament_ruleset = "EB25")
```

# Create skill tables

For this we need the dataset without stacked skills.

```{r}
create_skill_table(df_rosters1 %>% filter(roster.name %in% races), group_name = "Super league S6", tournament_ruleset = "EB25", return_table = FALSE)
```

# Create rosterbook

```{r eval = FALSE}
res <- file.copy(from = system.file("extdata", "EB25.jpg", package = "bbrosterplots"), to = "output/")


render_rosterbook(params = list(group_name = "Super League S6", 
                                tournament_ruleset = "EB25", 
                                cover_image = "EB25.jpg",
                                scale_cover_perc = "100%",                                
                                races = c("Khorne", "Dwarf"), 
                                perc = FALSE, 
                                team = FALSE), refresh_rmd = TRUE)
```

# Complete workflow

```{r eval = FALSE}
library(bbrosterplots)
# start with data in proper format
data(df_rosters)
data(df_rosters1)
# add skill color, cost and cluster sort order
df_rosters <- add_roster_metadata(df_rosters)
# create rosterplots
group_name <- unique(df_rosters$group_name)
create_rosterplot(df_rosters, group_name)
# create skill tables
create_skill_table(df_rosters1, return_table = FALSE)
# render PDF
render_rosterbook(params = list(group_name = group_name))
```

