---
title: "bbrosterplots"
date: "`r Sys.Date()`"
output:
  rmarkdown::github_document:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{bbrosterplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

# Load package

```{r}
library(bbrosterplots)
```

## Read example data

```{r}
data(df_rosters) 
data(df_rosters1)
group_name <- "Super League S6"
tournament_ruleset <- "EB25"
races <- unique(df_rosters$roster.name)
empty_out <- FALSE
```

## Current input data input format

```{r}
df_rosters %>% dplyr::filter(coach_name == "gsverhoeven")
```

# Add roster metadata

This adds:
* the cost for each player and inducement
* for each skill or skill stack a skill color

```{r}
df_rosters <- add_roster_metadata(df_rosters)
```

# Output folder cleaning

Optional step: Delete the output folder, then recreates it.

```{r}
if (empty_out) {
  unlink(tournament_ruleset, recursive = TRUE)
  dir.create(tournament_ruleset)
}
```

Subset races to speed up testing.

```{r}
races <- races[1:3]
df_rosters <- df_rosters %>%
  dplyr::filter(roster.name %in% races)

df_rosters1 <- df_rosters1 %>%
  dplyr::filter(roster.name %in% races)
```


## Create heatmap plots

```{r}
create_rosterplot(df_rosters, group_name)
```

# Create skill tables

For this we need the dataset without stacked skills.

```{r}
make_skill_table(df_rosters1, return_table = FALSE)
```

# Create rosterbook

```{r}
render_rosterbook()
```

# Complete workflow

```{r eval = FALSE}
library(bbrosterplots)
# start with data in proper format
data(df_rosters)
data(df_rosters1)
# add skill color, cost and cluster sort order
df_rosters <- add_roster_metadata(df_rosters)
# create rosterplots
group_name <- unique(df_rosters$group_name)
tournament_ruleset <- "EB25"
create_rosterplot(df_rosters, group_name)
# create skill tables
make_skill_table(df_rosters1, return_table = FALSE)
# render PDF
render_rosterbook()
```

